### 2016-11-16 paper/evaluation.tex
added content from sequential execution

To evaluate the frequency of time-consuming regression tests, we
considered the \Fix{X} Maven projects from Section~\ref{sec:subjects}
and compared the elapsed time to run their tests.  To avoid inflating
the measured time, we first compile the sources files (see
Figure~\ref{fig:mvn-execution}, line 1) and later (see
Figure~\ref{fig:mvn-execution}, line 2), we ran the tests ignoring
non-related tasks (\eg, \emph{javadoc} generation). In addition, when
we run a subject's test suite, we operate Maven in offline mode to
limit the network access, avoiding any unnecessary package update as
all required \emph{jars} are available locally. After the test
execution, we use a simple regular expression over the builder output
to extract the elapsed time.

\begin{figure}[h!]
\centering
\scriptsize
\lstset{
    escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
    morekeywords={o, DskipTests, Dmaven, javadoc, skip},
    deletekeywords={true}
}
\begin{lstlisting}
mvn clean install -DskipTests -Dmaven.javadoc.skip=true
mvn -o test -Dmaven.javadoc.skip=true
\end{lstlisting}
\caption{\label{fig:mvn-execution} Compiling and testing a Maven
    subject: line 1 compiles all subject's source artifacts and make
    them available in a local repository (\ie, directory \emph{.m2} in
    the user's home directory); line 2 runs the tests in offline mode
    ignoring javadoc generation.}
\end{figure}

We grouped the subjects according to the execution time: tests that
ran in less than one minute (\emph{short execution}), one to five
minutes (\emph{medium execution}), and more than five minutes
(\emph{long execution}).  Figure~\ref{fig:piechart-time} shows the
proportion of subjects per group.  Results indicate that a relatively
high number of projects from the sample set (\ie, 17\%) requires at
least five minutes to execute. The longest execution takes \Fix{x} to
finish. It is important to mention that Figure~\ref{fig:piechart-time}
represents a lower bound for elapsed time: some tests may finish early
due to a failure since the subjects were tested in a potentially
unstable revision.

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.4\textwidth]{results/rq1/plots/piechart.pdf}
    \caption{\label{fig:piechart-time} Subjects grouped by elapsed
    time on test execution ($t$): short execution ($t < 1m$), medium 
    execution ($1m \leq t < 5m$), and long execution ($5m \leq t$).}
\end{figure}

>>>>

To evaluate the frequency of time-consuming regression tests, we
considered the \Fix{X} Maven projects from Section~\ref{sec:subjects}
and compared the elapsed time to run their tests.  To avoid inflating
the measured time, we first compile the sources files (see
Figure~\ref{fig:mvn-execution}, line 1) and later (see
Figure~\ref{fig:mvn-execution}, line 2), we ran the tests ignoring
non-related tasks (\eg, \emph{javadoc} generation). In addition, when
we run a subject's test suite, we operate Maven in offline mode to
limit the network access, avoiding any unnecessary package update as
all required \emph{jars} are available locally. We also considered the
execution of all subjects enforcing sequential execution to avoid
having the real time cost masked by the use of any parallel setting
mentioned in Section~\ref{sec:modes}.  After the test execution, we
use a simple regular expression over the builder output to extract the
elapsed time.

\begin{figure}[h!]
\centering
\scriptsize
\lstset{
    escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
    morekeywords={o, DskipTests, Dmaven, javadoc, skip},
    deletekeywords={true}
}
\begin{lstlisting}
mvn clean install -DskipTests -Dmaven.javadoc.skip=true
mvn -o test -Dmaven.javadoc.skip=true
\end{lstlisting}
\caption{\label{fig:mvn-execution} Compiling and testing a Maven
    subject: line 1 compiles all subject's source artifacts and make
    them available in a local repository (\ie, directory \emph{.m2} in
    the user's home directory); line 2 runs the tests in offline mode
    ignoring javadoc generation.}
\vspace{-3ex}
\end{figure}

We grouped the subjects according to the execution time: tests that
ran in less than one minute (\emph{short execution}), one to five
minutes (\emph{medium execution}), and more than five minutes
(\emph{long execution}).  Figure~\ref{fig:piechart-time} shows the
proportion of subjects per group: on the left side, the pie chart
reports the results enforcing sequential execution; on the right side,
the results for the default execution.  Results indicate that a
relatively high number of projects from the sample set (\ie, 17\%)
requires at least five minutes to execute. The longest execution takes
\Fix{x} to finish. It is important to mention that
Figure~\ref{fig:piechart-time} represents a lower bound for elapsed
time: some tests may finish early due to a failure since the subjects
were tested in a potentially unstable revision.

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.4\textwidth]{results/rq1/plots/piechart.pdf}
    \caption{\label{fig:piechart-time} Subjects grouped by elapsed
    time on test execution ($t$): short execution ($t < 1m$), medium 
    execution ($1m \leq t < 5m$), and long execution ($5m \leq t$).
    \Fix{On the left side, results from sequential execution; the right side,
    results from default execution.}}
\end{figure}
